True versus apparent shapes of astrophysical bow shocks

### 2017-03-27 papers/Paper1/sec-quadrics-observations.tex
Add a couple of \clearpage commands
Before observation section and before conclusion, so that the figures
stay closer to the text that describes them.  We can remove them again
later when we have some more text

We developed a methodology for automatically tracing the arcs as follows:
\begin{enumerate}[1.]
\item Calculate arrays of celestial coordinates, \(C\), for each pixel
  of the image.
\item Using the central source coordinates, \(C_0\) and nominal
  bowshock radius, \(R_0\) from \citet{Kobulnicky:2016a}, construct a
  pixel mask that includes only those pixels with separations
  \(|C - C_0|\) from the source that lie between \(0.5 R_0\) and
  \(3 R_0\).  This mask will be used for all subsequent operations,
  which serves to help avoid confusion from the star itself and other
  bright sources in the field of view.
\item Define a ``step-back'' point, \(C_1\), which is located at a
  separation \(2 R_0\) from the source, but in the opposite direction
  from the apex of the bow shock. That is, along a position angle
  180\degr{} from the nominal position angle, \(\text{PA}_0\), of
  the bow shock axis.
\item Looping over a grid of 50 position angles, \(\text{PA}_k\), within
  \(\pm 60\degr\) of \(\text{PA}_0\), estimate the location of the
  arc along each PA from the step-back point via two different methods:
  \begin{enumerate}[(a)]
  \item The pixel with the maximum brightness, with coordinates
    \(C_{k,\text{peak}}\) (red dots in
    Fig.~\ref{fig:mipsgal-examples}).
  \item The mean brightness-weighted separation from \(C_1\), with
    coordinates \(C_{k,\text{mean}}\) (light blue dots in
    Fig.~\ref{fig:mipsgal-examples}).
  \end{enumerate}
  For each \(\text{PA}_k\) in the grid, the calculation is performed
  over only those pixels that satisfy
  \(|\text{PA}(C, C_1) - \text{PA}_k| < \frac12 \delta\theta\), where
  \(\delta\theta = 120/50 = 2.4\degr\), which defines a thin radial wedge from
  \(C_1\).
\item For each of the points \(C_{k,\text{peak}}\) and \(C_{k,\text{mean}}\), determine the separation from the central source, \(R_k = |C_k - C_0|\) and the angle from the bow shock axis about the central source \(\theta_k = \text{PA}(C_k, C_0) - \text{PA}_0\)

>>>>

We developed a methodology for automatically tracing the arcs as follows:
\begin{enumerate}[1.]
\item Calculate arrays of celestial coordinates, \(C\), for each pixel
  of the image.
\item Using the central source coordinates, \(C_0\) and nominal
  bowshock radius, \(R_0\) from \citet{Kobulnicky:2016a}, construct a
  pixel mask that includes only those pixels with separations
  \(|C - C_0|\) from the source that lie between \(0.5 R_0\) and
  \(3 R_0\).  This mask will be used for all subsequent operations,
  which serves to help avoid confusion from the star itself and other
  bright sources in the field of view.
\item Define a ``step-back'' point, \(C_1\), which is located at a
  separation \(2 R_0\) from the source, but in the opposite direction
  from the apex of the bow shock. That is, along a position angle
  180\degr{} from the nominal position angle, \(\text{PA}_0\), of
  the bow shock axis.
\item Looping over a grid of 50 position angles, \(\text{PA}_k\), within
  \(\pm 60\degr\) of \(\text{PA}_0\), estimate the location of the
  arc along each PA from the step-back point via two different methods:
  \begin{enumerate}[(a)]
  \item The pixel with the maximum brightness, with coordinates
    \(C_{k,\text{peak}}\) (red dots in
    Fig.~\ref{fig:mipsgal-examples}).
  \item The mean brightness-weighted separation from \(C_1\), with
    coordinates \(C_{k,\text{mean}}\) (light blue dots in
    Fig.~\ref{fig:mipsgal-examples}).
  \end{enumerate}
  For each \(\text{PA}_k\) in the grid, the calculation is performed
  over only those pixels that satisfy
  \(|\text{PA}(C, C_1) - \text{PA}_k| < \frac12 \delta\theta\), where
  \(\delta\theta = 120/50 = 2.4\degr\), which defines a thin radial wedge from
  \(C_1\).
\item For each of the points \(C_{k,\text{peak}}\) and \(C_{k,\text{mean}}\), determine the radial separation from the central source, \(R_k = |C_k - C_0|\) and the angle from the bow shock axis about the central source \(\theta_k = \text{PA}(C_k, C_0) - \text{PA}_0\).  These are plotted in the upper left panels of  Figure~\ref{fig:mipsgal-examples}.
